---
title: "WKPHM Advice Template"
author: "WKPHM"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
library(sf)
library(rnaturalearth)
library(ggplot2)
library(ncdf4)
library(rgdal)
library(rgeos)
library(gstat)
library(maptools)
library(raster)
library(corrplot)
library(dismo)
library(PresenceAbsence)
library(AICcmodavg)
library(gridExtra)
library(viridis)
library(googledrive)
source("VarianceInflationFactors.R")
dir.create("Figures")
dir.create("Predictions")
knitr::opts_chunk$set(echo = TRUE)
```
## Purpose

The objective of this piece of code was to develop a relatively simple model for a species of coral that could be used to demonstrate the pieces of the proposed ICES PHM advice template. The species chosen was *Acanthogorgia armata*. It was chosen simply because it had a fairly large number of observations in the ICES VME database. This is not meant to be a realistic model of the distribution of *Acanthogorgia armata*, but is instead used here to generate the components of an PHM (data, model, residuals) that can be used to evaluate its predictions and utility.

## Dependent data

The dependent data for *Acanthogorgia armata* were observations of presence or absence in the open ICES VME database. In total there were 901 observations of presence in the database. In the code below the counts for the species are also included in the data that is generated, but these were not used in the modeling at this time. Absences were inferred from sample locations where observations for other species were made, but *Acanthogorgia armata* were not recorded. In total there were > 30,000 absences in the ICES VME database.

The code below does the following

1. Import the dependent data from the open ICES data base
2. Calculates a mean depth for each observation where an upper and lower depth were recorded
3. Compiles a data frame of the unique observation locations (by their recorded middle latitude and longitude)
4. Subsets all the records where *Acanthogorgia armata* was observed and assigns them a presence (0) and sums any counts that were recorded at the location (or provides count = 1 where no count was provided, but presence was noted)
5. Merges those presence records with the entire database and assigns presence and counts = 0 to the records with no presence observation
6. There was a single duplicate record for this sp

```{r importdata,results='hide',message=FALSE,warning=FALSE}
VME_data<-read.csv("vme_open_extraction11012021.csv",header=TRUE,stringsAsFactors=FALSE) #Import the entire database
VME_data$Depth<-abs((as.numeric(VME_data$DepthLower)+as.numeric(VME_data$DepthUpper))/2) #Generate a mean depth for each point (where depths were collected) based on the upper and lower recorded depths
All_depths<-aggregate(Depth~MiddleLatitude+MiddleLongitude,data=VME_data,FUN="mean",na.rm=TRUE) #Aggregate these depths to each position in the database
dim(VME_data)
dim(All_depths)

rev(sort(table(VME_data$Species)))
All_points<-unique(data.frame(Longitude=VME_data$MiddleLongitude,Latitude=VME_data$MiddleLatitude)) #Generate the unique positions of all the observations in the database
All_points<-All_points[All_points$Latitude!=0,] # Remove a record with Latitude and Longitude = 0. This is likely an error
dim(All_points)

All_points<-merge(All_points,All_depths,by.x=c("Longitude","Latitude"),by.y=c("MiddleLongitude","MiddleLatitude"),all.x=TRUE) #Add the depth values to the unique position set

Acanth_arm<-subset(VME_data,VME_data$Species=="Acanthogorgia armata") #Subset the data for a species of interest
Acanth_arm<-data.frame(ICES_ID=Acanth_arm$ï..ICES_ID,Species=Acanth_arm$Species,Longitude=Acanth_arm$MiddleLongitude,Latitude=Acanth_arm$MiddleLatitude,Presence=1,Number=as.numeric(Acanth_arm$Number)) #Create a data frame of the minimal data for presence of the species, positions and numbers observed
Acanth_arm<-merge(All_points,Acanth_arm,by=c("Longitude","Latitude"),all.x=TRUE) #Merge the species data with the full set of observation points
Acanth_arm$Species<-"Acanthogorgia armata" # Fill the Species column
Acanth_arm$Presence[is.na(Acanth_arm$Presence)]<-0 #Add zeros for absence at those observation points where the species of interest was not recorded (these are now absences)
Acanth_arm$Number[is.na(Acanth_arm$Number)]<-0 # Add zeros for number column at those observation points where the species of interst was not recorded
dim(Acanth_arm)
dim(All_points) # These two data frames should have the same number of rows. For this species, the numbers don't match, which means there is a duplicate record at a Lat-long pair for the species

which(duplicated(cbind(Acanth_arm$Latitude,Acanth_arm$Longitude))) # find which record is duplicated
which(duplicated(cbind(Acanth_arm$Latitude,Acanth_arm$Longitude),fromLast=TRUE)) #find the other record that is duplicated
Acanth_arm[13705:13706,] # Look to see whats happening. It looks like there is one record with number = 1 and one with number = 3,
Acanth_arm[13705,"Number"]<-4 # Change 1 record to reflect the total number observed at that position
Acanth_arm<-Acanth_arm[-13706,] # Delete the remaining record
dim(Acanth_arm)

#table(Acanth_arm$Presence) # See how many presences (1) and absences (0) there are in the data


```

```{r MapThePoints,message=FALSE,warning=FALSE}
#IMPORT A BASEMAP AND TRANSFORM TO A NICER PROJECTION FOR THE NORTH ATLANTIC
bg = ne_countries(scale = "medium",  returnclass = "sf")
p<-ggplot()+
  #basemap
  geom_sf(data = bg)+
  coord_sf(xlim = range(Acanth_arm$Longitude, na.rm = TRUE), 
           ylim = range(Acanth_arm$Latitude, na.rm = TRUE), 
           expand = TRUE)+
  
  # add points
  geom_point(data = Acanth_arm, 
             aes(x=Longitude,y=Latitude,group=as.factor(Presence),color=as.factor(Presence)),
             alpha = 0.7, shape=21, size = 2)+
  
  # formatting
  scale_fill_viridis_d(option = "inferno")+
  scale_color_viridis_d(option = "inferno")+
  labs(x=NULL, y=NULL, 
       fill = 'Presence', 
       color = 'Presence')+
  theme_dark()+
  theme(panel.grid = element_blank())

print(p)
```

## Explanatory variables

NOTE: This section of code is for reference only. I have not provided the raw data from GEBCO or World Ocean Atlas since the files are so large and take so much time to process. I can provide these on request (Chris Rooper).

```{r pressure, eval=FALSE}
# bathy<-raster("GEBCO_bathy.tif")
# newproj<-crs(bathy)
# ICES_regions<-readOGR("Shapefiles","ICES_Areas_20160601_cut_dense_3857")
# ICES_regions<-spTransform(ICES_regions,newproj)
# ICES_regions3<-subset(ICES_regions,as.numeric(as.character(ICES_regions$SubArea))>5&as.numeric(as.character(ICES_regions$SubArea))<13)
# plot(bathy)
# plot(ICES_regions3,add=TRUE,border="red")
# points(cbind(Acanth_arm$Longitude[Acanth_arm$Presence==1],Acanth_arm$Latitude[Acanth_arm$Presence==1]),pch=20,col="purple")
# 
# ICES_bathy<-crop(bathy,ICES_regions3,progress="text",overwrite=TRUE,filename="ICES_bathy3")
# ICES_bathy[ICES_bathy>0]<-NA
# ICES_bathy<-ICES_bathy*-1
# writeRaster(ICES_bathy,"ICES_bathy3",overwrite=TRUE)
# plot(ICES_bathy)
# 
# file1<-nc_open("woa18_all_o00_01.nc")
# O2<-ncvar_get(file1,varid="o_an",collapse_degen = FALSE)
# Lat<-as.vector(ncvar_get(file1,varid="lat"))
# Lon<-as.vector(ncvar_get(file1,varid="lon"))
# Depth<-as.vector(ncvar_get(file1,varid="depth"))
# Lon1<-rep(Lon,length(Lat)*length(Depth))
# Lat1<-rep(rep(Lat,each=length(Lon)),length(Depth))
# Depth1<-rep(rep(Depth,each=length(Lon)),each=length(Lat))
# O2<-as.vector(ncvar_get(file1,varid="o_an"))
# O2_data<-data.frame(Longitude=Lon1,Latitude=Lat1,Depth=Depth1)
# t1<-which(O2_data$Latitude>=30&O2_data$Latitude<=87&O2_data$Longitude>=-80&O2_data$Longitude<=60)
# O2_data<-data.frame(Longitude=Lon1[t1],Latitude=Lat1[t1],Depth=Depth1[t1],O2=O2[t1])
# O2_data<-subset(O2_data,O2_data$O2>=0)
# O2_depth<-aggregate(Depth~Longitude+Latitude,data=O2_data,FUN="min")
# O2_data<-merge(O2_depth,O2_data,by=c("Longitude","Latitude","Depth"))
# nc_close(file1)
# 
# O2.project<-SpatialPointsDataFrame(coords=c(O2_data["Longitude"],O2_data["Latitude"]),data=O2_data["O2"], proj4string=newproj) 
# t1<-which(raster::extract(ICES_bathy,O2.project)>0)
# O2.project<-O2.project[t1,]
# 
# #				Interpolate to raster
# O2.idw<-gstat(id = "O2", formula = O2~1, data=O2.project, nmax=8, set=list(idp = 2.5))
# O2.raster<-interpolate(ICES_bathy,O2.idw,overwrite=TRUE,xyOnly=TRUE,filename="O2raster", progress="text")
# 
# O2.raster<-mask(O2.raster,ICES_bathy,overwrite=TRUE, filename="O2raster2")
# plot(O2.raster)
# 
# O2.raster<-aggregate(O2.raster,fact=2,filename="O2",FUN="mean",progress="text",overwrite=TRUE)
# bathy<-aggregate(ICES_bathy,fact=2,filename="bathy",FUN="mean",progress="text",overwrite=TRUE)

```

```{r stackandextract,message=FALSE,warning=FALSE}

temp <- tempfile(fileext = ".zip")
drive_deauth()
drive_download(as_id("1k0j9yTDFAme0zwxRLOJtrip3TXjKI9L6"), path = temp, overwrite = TRUE)
unzip(temp,overwrite=TRUE)

ICES_bathy<-raster("./ICES_variables/bathy")
ICES_slope<-terrain(ICES_bathy,opt="slope",progress="text",overwrite=TRUE)
ICES_TPI<-terrain(ICES_bathy,opt="tpi",progress="text",overwrite=TRUE)
O2.raster<-raster("./ICES_variables/O2")
raster.stack<-stack(ICES_bathy,ICES_slope,ICES_TPI,O2.raster)
names(raster.stack)<-c("bathy","slope","TPI","O2")
variables<-data.frame(raster::extract(raster.stack,cbind(Acanth_arm$Longitude,Acanth_arm$Latitude)))
Acanth_arm<-cbind(Acanth_arm,variables)
variables<-subset(variables,variables$bathy>0)
Acanth_arm<-subset(Acanth_arm,Acanth_arm$bathy>0)

newproj<-crs(ICES_bathy)
ICES_regions<-readOGR("./ICES_variables/Shapefiles","ICES_Areas_20160601_cut_dense_3857")
ICES_regions<-spTransform(ICES_regions,newproj)
ICES_regions3<-subset(ICES_regions,as.numeric(as.character(ICES_regions$SubArea))>5&as.numeric(as.character(ICES_regions$SubArea))<13)
```

### Collinearity


```{r lookforcollinearity,message=FALSE,warning=FALSE}
plot(raster.stack)

cormat1<-cor(variables,use="complete.obs")
corrplot(cormat1,method="number",type="lower")
print(corvif(variables))

```

## Model building

### Model fitting
```{r buildsimplemodel,message=FALSE,warning=FALSE}
TableData<-data.frame(Fold=character(),AIC=numeric(),threshold=numeric(),AUC_training=numeric(),AUC_testing=numeric(),TSS_training=numeric(),TSS_testing=numeric(),Cor_training=numeric(),Cor_testing=numeric(),RMSE_training=numeric(),RMSE_testing=numeric(),stringsAsFactors=FALSE)

Acanth.GLM.pa<-glm(Presence~bathy+slope+TPI+O2+I(bathy^2)+I(slope^2)+I(TPI^2)+I(O2^2),data=Acanth_arm,family=binomial)
summary(Acanth.GLM.pa)

#Stepwise reduction based on AIC
Acanth.GLM.pa<-glm(Presence~slope+TPI+O2+I(slope^2)+I(TPI^2)+I(O2^2),data=Acanth_arm,family=binomial)
summary(Acanth.GLM.pa)


######TEST THE PREDICTIONS AGAINST THE TRAINING DATA############################
TableData[1,1]<-"Full model"
train.auc_data<-data.frame(cbind(seq(1,length(Acanth.GLM.pa$y),1),Acanth.GLM.pa$y,Acanth.GLM.pa$fitted.values))
##Calculate the AUC
TableData[1,4]<-round(auc(train.auc_data,na.rm=TRUE)[1],3)
#Calculate the RMSE
TableData[1,10]<-round(sqrt(mean((train.auc_data$X2-train.auc_data$X3)^2)),3)
#Calculate the TSS
train.threshold<-optimal.thresholds(train.auc_data,opt.methods=3)[1,2]
TableData[1,3]<-train.threshold
TableData[1,6]<-round(sensitivity(cmx(train.auc_data,threshold=train.threshold))+specificity(cmx(train.auc_data,threshold=train.threshold))-1,3)[1]
#Calculate the Spearmans Rank correlation
TableData[1,8]<-round(cor.test(train.auc_data[,2],train.auc_data[,3],method="spearman")$estimate,3)
#AIC
TableData[1,2]<-Acanth.GLM.pa$aic

print(cmx(train.auc_data,threshold=train.threshold))

#RESPONSE CURVE PLOTS
## generate prediction frame
TPIframe <- data.frame(TPI=seq(min(Acanth_arm$TPI,na.rm=TRUE),max(Acanth_arm$TPI,na.rm=TRUE),length=51),O2=median(Acanth_arm$O2,na.rm=TRUE),slope=median(Acanth_arm$slope,na.rm=TRUE))
TPIframe$predicted <- predict(Acanth.GLM.pa,newdata=TPIframe,type="response",se.fit=TRUE)$fit
TPIframe$se.fit <- predict(Acanth.GLM.pa,newdata=TPIframe,type="response",se.fit=TRUE)$se.fit

p3<-ggplot(TPIframe)+geom_ribbon(aes(x=TPI,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=TPI,y=predicted))+xlab("Topographic position index")+ylab("Probability of presence")


O2frame <- data.frame(O2=seq(min(Acanth_arm$O2,na.rm=TRUE),max(Acanth_arm$O2,na.rm=TRUE),length=51),slope=median(Acanth_arm$slope,na.rm=TRUE),TPI=median(Acanth_arm$TPI,na.rm=TRUE))
O2frame$predicted <- predict(Acanth.GLM.pa,newdata=O2frame,type="response",se.fit=TRUE)$fit
O2frame$se.fit <- predict(Acanth.GLM.pa,newdata=O2frame,type="response",se.fit=TRUE)$se.fit

p1<-ggplot(O2frame)+geom_ribbon(aes(x=O2,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=O2,y=predicted))+xlab("Oxygen")+ylab("Probability of presence")

slopeframe <- data.frame(slope=seq(min(Acanth_arm$slope,na.rm=TRUE),max(Acanth_arm$slope,na.rm=TRUE),length=51),O2=median(Acanth_arm$O2,na.rm=TRUE),TPI=median(Acanth_arm$TPI,na.rm=TRUE))
slopeframe$predicted <- predict(Acanth.GLM.pa,newdata=slopeframe,type="response",se.fit=TRUE)$fit
slopeframe$se.fit <- predict(Acanth.GLM.pa,newdata=slopeframe,type="response",se.fit=TRUE)$se.fit

p2<-ggplot(slopeframe)+geom_ribbon(aes(x=slope,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=slope,y=predicted))+xlab("Slope")+ylab("Probability of presence")

#plot it
png("./Figures/response_curvesFull.png",width=8,height=6,units="in",res=300)
grid.arrange(p1,p2,p3,ncol=1)
dev.off()

####FIGURE 3 - MAXENT DIAGNOSTICS PLOTS
#Plots for data
png(filename="./Figures/GLMdiagnosticsFull.png",width=6,height=6,res=300,units="in")
par(mfcol=c(2,2),family="sans",mar=c(4,4,1,.01))
auc.roc.plot(train.auc_data,opt.methods=2,main="",add.legend=F,xlab="Specificity",ylab="Sensitivity",add.opt.legend=F)
calibration.plot(train.auc_data,N.bins=10,xlab="Predicted occurence",ylab="Proportion of observed occurence",main="")
presence.absence.hist(train.auc_data,truncate.tallest=TRUE,main="",ylab="Number of observations",xlab="Predicted probability")
dev.off()


```

### Model predictions
```{r simplemodelpredictions,message=FALSE,warning=FALSE}

#######MAKE THE PREDICTION RASTER ##############################################
#Predict the model to a raster to see where suitable habitat is predicted
Acanth.GLM.pa.raster<-predict(raster.stack, Acanth.GLM.pa,filename="./Predictions/GLMFull",fun=predict, na.rm=TRUE,overwrite=TRUE,progress="text",type="response",newdata.guaranteed=TRUE)


png(filename="./Figures/ProbabilityMapFull.png",width=6,height=6.5,res=300,units="in")
par(mfrow=c(1,1),mar=c(5,4,1,1),family="sans")
plot(Acanth.GLM.pa.raster, main = "", box=F,col = viridis(255),ext=ICES_regions3,legend.shrink=0.5,axis.args=list(cex.axis=0.65),legend.args=list(text="Probability of presence",cex=0.65,cex.lab=0.65,side=1,line=2),horiz=TRUE,ylab="Latitude",xlab="Longitude")
dev.off()

```

## Model validation

```{r simplemodelvalidation,message=FALSE,warning=FALSE}
##Sample training and testing data sets####
Acanth_arm$Group<-kfold(Acanth_arm,k=5)

foldlist<-vector(mode="list",length=5)

###LOOP THROUGH THE FOLDS####
for(i in 1:5){
training.data<-subset(Acanth_arm,Acanth_arm$Group!=i)
test.data<-subset(Acanth_arm,Acanth_arm$Group==i)

#######MAKE THE MODELS#############
Acanth.GLM.paf<-glm(Presence~slope+O2+TPI+I(slope^2)+I(O2^2)+I(TPI^2),data=training.data,family=binomial)
summary(Acanth.GLM.pa)
foldlist[[i]]<-Acanth.GLM.paf
names(foldlist[i])<-paste0("AcanthGLMFold",i)

######TEST THE PREDICTIONS AGAINST THE TRAINING DATA############################
TableData[i+1,1]<-paste0("GLMFold_",i)
train.auc_dataf<-data.frame(cbind(seq(1,length(Acanth.GLM.paf$y),1),Acanth.GLM.paf$y,Acanth.GLM.paf$fitted.values))
##Calculate the AUC
TableData[i+1,4]<-round(auc(train.auc_dataf,na.rm=TRUE)[1],3)
#Calculate the RMSE
TableData[i+1,10]<-round(sqrt(mean((train.auc_dataf$X2-train.auc_dataf$X3)^2)),3)
#Calculate the TSS
train.thresholdf<-optimal.thresholds(train.auc_dataf,opt.methods=3)[1,2]
TableData[i+1,3]<-train.thresholdf
TableData[i+1,6]<-round(sensitivity(cmx(train.auc_dataf,threshold=train.thresholdf))+specificity(cmx(train.auc_dataf,threshold=train.thresholdf))-1,3)[1]
#Calculate the Spearmans Rank correlation
TableData[i+1,8]<-round(cor.test(train.auc_dataf[,2],train.auc_dataf[,3],method="spearman")$estimate,3)
#AIC
TableData[i+1,2]<-Acanth.GLM.paf$aic

print(cmx(train.auc_dataf,threshold=train.thresholdf))

######TEST THE PREDICTIONS AGAINST THE TEST DATA############################
pred<-predict(Acanth.GLM.paf,newdata=test.data,type="response")
test.auc_dataf<-data.frame(cbind(seq(1,length(test.data$Presence),1),test.data$Presence,pred))
test.auc_dataf<-subset(test.auc_dataf,test.auc_dataf$pred>=0)
##Calculate the AUC
TableData[i+1,5]<-round(auc(test.auc_dataf,na.rm=TRUE)[1],3)
#Calculate the RMSE
TableData[i+1,11]<-round(sqrt(mean((test.auc_dataf$V2-test.auc_dataf$pred)^2)),3)
#Calculate the TSS
TableData[i+1,7]<-round(sensitivity(cmx(test.auc_dataf,threshold=train.thresholdf))+specificity(cmx(test.auc_dataf,threshold=train.thresholdf))-1,3)[1]
#Calculate the Spearmans Rank correlation
TableData[i+1,9]<-round(cor.test(test.auc_dataf[,2],test.auc_dataf[,3],method="spearman")$estimate,3)

print(cmx(test.auc_dataf,threshold=train.thresholdf))

#RESPONSE CURVE PLOTS
## generate prediction frame
TPIframe <- data.frame(TPI=seq(min(Acanth_arm$TPI,na.rm=TRUE),max(Acanth_arm$TPI,na.rm=TRUE),length=51),O2=median(Acanth_arm$O2,na.rm=TRUE),slope=median(Acanth_arm$slope,na.rm=TRUE))
TPIframe$predicted <- predict(Acanth.GLM.paf,newdata=TPIframe,type="response",se.fit=TRUE)$fit
TPIframe$se.fit <- predict(Acanth.GLM.paf,newdata=TPIframe,type="response",se.fit=TRUE)$se.fit

p3<-ggplot(TPIframe)+geom_ribbon(aes(x=TPI,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=TPI,y=predicted))+xlab("Topographic position index")+ylab("Probability of presence")

O2frame <- data.frame(O2=seq(min(Acanth_arm$O2,na.rm=TRUE),max(Acanth_arm$O2,na.rm=TRUE),length=51),slope=median(Acanth_arm$slope,na.rm=TRUE),TPI=median(Acanth_arm$TPI,na.rm=TRUE))
O2frame$predicted <- predict(Acanth.GLM.paf,newdata=O2frame,type="response",se.fit=TRUE)$fit
O2frame$se.fit <- predict(Acanth.GLM.paf,newdata=O2frame,type="response",se.fit=TRUE)$se.fit

p1<-ggplot(O2frame)+geom_ribbon(aes(x=O2,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=O2,y=predicted))+xlab("Oxygen")+ylab("Probability of presence")

slopeframe <- data.frame(slope=seq(min(Acanth_arm$slope,na.rm=TRUE),max(Acanth_arm$slope,na.rm=TRUE),length=51),O2=median(Acanth_arm$O2,na.rm=TRUE),TPI=median(Acanth_arm$TPI,na.rm=TRUE))
slopeframe$predicted <- predict(Acanth.GLM.paf,newdata=slopeframe,type="response",se.fit=TRUE)$fit
slopeframe$se.fit <- predict(Acanth.GLM.paf,newdata=slopeframe,type="response",se.fit=TRUE)$se.fit

p2<-ggplot(slopeframe)+geom_ribbon(aes(x=slope,ymin=predicted-se.fit,ymax=predicted+se.fit),fill="grey70") + geom_line(aes(x=slope,y=predicted))+xlab("Slope")+ylab("Probability of presence")

#plot it
png(paste0("./Figures/response_curvesfold",i,".png"),width=8,height=6,units="in",res=300)
grid.arrange(p1,p2,p3,ncol=1)
dev.off()

####FIGURE 3 - MAXENT DIAGNOSTICS PLOTS
#Plots for data
png(filename=paste0("./Figures/GLMdiagnosticsfold",i,".png"),width=6,height=6,res=300,units="in")
par(mfcol=c(2,2),family="sans",mar=c(4,4,1,.01))
auc.roc.plot(train.auc_data,opt.methods=2,main="",add.legend=F,xlab="Specificity",ylab="Sensitivity",add.opt.legend=F)
calibration.plot(train.auc_data,N.bins=10,xlab="Predicted occurence",ylab="Proportion of observed occurence",main="")
presence.absence.hist(train.auc_data,truncate.tallest=TRUE,main="",ylab="Number of observations",xlab="Predicted probability")
dev.off()

Acanth.GLM.pa.rasterf<-predict(raster.stack, Acanth.GLM.paf,filename=paste("./Predictions/GLMFold",i,sep=""),fun=predict, na.rm=TRUE,overwrite=TRUE,progress="text",type="response",newdata.guaranteed=TRUE)


png(filename=paste0("./Figures/ProbabilityMapFold",i,".png"),width=6,height=6.5,res=300,units="in")
par(mfrow=c(1,1),mar=c(5,4,1,1),family="sans")
plot(Acanth.GLM.pa.rasterf, main = "", box=F,col = viridis(255),ext=ICES_regions3,legend.shrink=0.5,axis.args=list(cex.axis=0.65),legend.args=list(text="Probability of presence",cex=0.65,cex.lab=0.65,side=1,line=2),horiz=TRUE,ylab="Latitude",xlab="Longitude")
dev.off()
}

```


## Model uncertainty

### Spatial patterns in residuals

```{r mapmodeluncertainty,message=FALSE,warning=FALSE}
##################################################################

Acanth.GLM.padata<-subset(Acanth.GLM.pa$data,Acanth.GLM.pa$data$slope>=0)
Acanth.GLM.padata$residuals<-Acanth.GLM.pa$residuals

p<-ggplot()+
  #basemap
  geom_sf(data = bg)+
  coord_sf(xlim = range(Acanth.GLM.padata$Longitude, na.rm = TRUE), 
           ylim = range(Acanth.GLM.padata$Latitude, na.rm = TRUE), 
           expand = TRUE)+
  
  # add points
  geom_point(data = Acanth.GLM.padata, 
             aes(x=Longitude,y=Latitude,fill=residuals),
             alpha = 0.7, shape=21, size = 2)+
  
  # formatting
  scale_fill_viridis_c(option = "magma")+
  scale_color_viridis_c(option = "magma")+
  theme_dark()+
  theme(panel.grid = element_blank())

png(filename="./Figures/Residuals.png",width=6,height=7,res=300,units="in")
print(p)
dev.off()


#Calculate prediction error and SE

F1<-raster("./Predictions/GLMFold1")
F2<-raster("./Predictions/GLMFold2")
F3<-raster("./Predictions/GLMFold3")
F4<-raster("./Predictions/GLMFold4")
F5<-raster("./Predictions/GLMFold5")
Error.stack<-stack(F1,F2,F3,F4,F5)
#plot(Error.stack)
Prediction.se<-calc(Error.stack,fun=sd)

png(filename="./Figures/Fullmapse.png",width=6,height=7,res=300,units="in")
par(mfrow=c(1,1),mar=c(5,4,1,1),family="sans")
plot(Prediction.se, main = "", box=F,col = colorRampPalette(c("darkgreen","coral"))(30),ext=ICES_regions3,legend.shrink=0.5,axis.args=list(cex.axis=0.65),legend.args=list(text="Prediction standard error",cex=0.65,cex.lab=0.65,side=1,line=2),horiz=TRUE,ylab="Latitude",xlab="Longitude")
dev.off()

```


